Balsa: A Compact Line Notation Based on SMILES

### 2022-07-01 manuscript.tex
Adds figure for PPB bond placement. closes #8
Adds figure for assigning PPBs. closes #9

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Partial Parity Bond Placement.}
    \label{fig:ppb-placement}
\end{figure}

@@

The same procedure works in reverse when encoding the \ttt{direction} attribute. 2-butene having the \textit{anti} conformation is modeled using a diagram whose left- and right-hand sides point downward and upward, respectively. The parent atom, a primary carbon, is identified. It is bonded to one neighbor through a PPB. To match the diagram, a direction of \ttt{Up} is assigned. The child atom is attached to its own child through a double bond. Finally, the grandchild is attached to its own child through a PPB whose direction is consistent with the diagram. A direction of \ttt{Up} is therefore assigned.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Assigning partial parity bonds to \textit{anti}-2-butene.}
    \label{fig:assigning-ppb}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{partial-parity-bond-placement.pdf}
    \caption{Partial Parity Bond Placement. Two unique modes of PPB placement are \textit{syn} and \textit{anti} (left and right, respectively). Within each mode is an equivalent pair of PPB pairs.}
    \label{fig:ppb-placement}
\end{figure}

@@

The same procedure works in reverse when encoding the \ttt{direction} attribute (Figure~\ref{fig:assigning-ppb}). 2-butene having the \textit{anti} conformation is modeled using a diagram whose left- and right-hand sides point downward and upward, respectively. The parent atom, a primary carbon, is identified. It is bonded to one neighbor through a PPB. To match the diagram, a direction of \ttt{Up} is assigned. The child atom is attached to its own child through a double bond. Finally, the grandchild is attached to its own child through a PPB whose direction is consistent with the diagram. A direction of \ttt{Up} is therefore assigned.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{assigning-ppbs.pdf}
    \caption{Assigning partial parity bonds to \textit{cis}-2-butene.}
    \label{fig:assigning-ppb}
\end{figure}
